A Recipe for Scavenging - the natural history of a behaviour

### 2016-04-27 natural history of scavenging.tex
updated figure
Figures legends update

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Summary_figure/Summary_figure_Landscape.pdf}
\caption{Factors influencing the proportion of scavenging in a vertebrates' diet. Blue lines indicate a reduction in the factor and red lines indicate an increase.}
%TG: Probably needs some more explanations...
\label{Summary_figure}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{timeline_figure/timeLine.pdf}
\caption{The diversity of scavengers through time. Each species has either direct evidence for it being a scavenger or would be positioned high up on our scavenging scale.}
\label{Timeline}
\end{figure}

>>>>

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Summary_figure/Summary_figure.pdf}
\caption{Factors influencing the proportion of scavenging in a vertebrates' diet. The black and white gradient bar on the top represent the proportion of scavenging in the diet, ranging from low (- -) on the left hand side to high (+ +) on the right hand side. Blue lines indicate that a reduction in the factor will lead to more or less proportion of scavenging in the diet and red lines indicate an increase.}
%Silhouettes from left to right on each line: \textit{Somelizard ofsomesort}, \textit{Felis silvestris}, \textit{Somelizard ofsomesort}, Diomedeidae, \textit{Antennarius striatus}, \textit{Gyps}, Actinopterigii skeleton, \textit{Stegosaurus} skeleton, \textit{Gyps}, \textit{Crocuta crocuta}, \textit{Rousettus aegyptiacus}, \textit{Crocuta crocuta}.
\label{Summary_figure}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{timeline_figure/timeLine.pdf}
\caption{The diversity of scavengers through time. Each species has either direct evidence for it being a scavenger or would be positioned high up on our scavenging scale. The three lines represent the three different environments (from top to bottom: aerial, terrestrial and aquatic). Time is represented on the horizontal axis with each third representing respectively the Paleozoic (541 to 252 Mya), the Mesozoic (252 to 66 Mya) and the Cenozoic (66 Mya to the present).}
%Silhouettes from left to right in each different environment: Aerial: \textit{Some pterosaur}, Azhdarchid (which one?), Diomedeidae, \textit{Gyps}, \textit{Some preybird}; Terrestrial: \textit{Some mammaliaform?}, \textit{Some temnospondyl?}, \textit{Allosaurus}?, \textit{Dilophosaurus}?, \textit{Canis lupus?}, \textit{Crocuta crocuta}, \textit{Some shneakyshnake}, \textit{Homo sapiens}; Aquatic: \textit{Tiktaalik}, \textit{Some antiarchplacoderm}, Ichtyosauridae, \textit{Some metriorhynchidae?}, Mosasauridae, \textit{Basilosaurus}, \textit{Carcharodon carcharias}, \textit{Orcinus orca}.
\label{Timeline}
\end{figure}
